\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

	\addtolength{\oddsidemargin}{-.475in}
	\addtolength{\evensidemargin}{-.475in}
	\addtolength{\textwidth}{1.00in}

	\addtolength{\topmargin}{-.475in}
	\addtolength{\textheight}{1.00in}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Joseph} % Your first name
\familyname{Allen} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Block C Alto}{Salford, M3 6GD}
\mobile{07871556664}
\email{joseph.allen.1994@hotmail.com}
\homepage{github.com/joezcool02}{} % The first argument is the URL for the clickable link, the second argument is the URL displayed in the template - this allows special characters to be displayed such as the tilde in this example

%----------------------------------------------------------------------------------------

\begin{document}



%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage

\recipient{BOLD TEXT REPLACE}{COMPANY NAME\\ADDRESS 1\\ADDRESS 2,CITY} % Letter recipient
\date{\today} % Letter date
\opening{Dear Sir or Madam,} % Opening greeting
\closing{Sincerely yours,} % Closing phrase
\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

\makelettertitle % Print letter title

I am pleased to present my application for a position at COMPANY NAME. MAYBE WRITE SOMETHING IMPORTANT TO THE INDIVIDUAL APPLICATION HERE.

I am a Manchester based Web Developer who studied Computer Science and Maths with Industrial Experience at the University of Manchester. I have been a Web Developer since my first year at University where I decided to start my own Web Development firm and I am now aspiring to become a Lead Developer. I spend my free time doing a variety of Digital things including exploring Digital Art, Digital Marketing and participating in Data Science competitions.

I am a strong believer in AGILE methodologies, while appreciating that other methods have their place, and have used SCRUM and Kanban professionally. I hold a firm belief that User Experience and Data Science are the key to the future of Web Development and am always keen to bring these aspects into my development when appropriate. I am confident in running Retrospectives, Stand-ups and reflective meetings as I believe these are vital for improving team happiness and love opportunities to apply these methods.

I have organized events of many scale from small Digital Art meet-ups to much larger scale University events with over 500 attendees. I am always eager to take part in events such as MancJS and UXMentors and bring any learnings back into the business where possible.

I am always looking for smarter ways to work and have welcomed Less or Sass as replacements for CSS and am currently enjoying the turbulent time the Front-end frameworks are experiencing, personally enjoying React as I have a strong Node background.

Thank you very much for your time and I am thankful for the opportunity of being considered for this position.

Hope to hear from you soon.

\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------
\clearpage



\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{2013--Current}{Bachelor of Computer Science and Mathematics}{The University of Manchester}{}{\textit{First year  -- 73.1\%}}{Currently in second year.}
\cventry{2011--2013}{A-level}{Tanglin Trust School}{Singapore}{Computer Science - A , Mathematics - A, Further Mathematics - B, Physics - B, AS Economics - B}{}  % Arguments not required can be left empty


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}


\cventry{2013--Current}{Tutor}{\textsc{Tutor Trust}}{Manchester}{}{I go into local schools and teach children the fundamentals of programming using the Scratch programming language. I have a passion for teaching and learning and this is critical as Computer Science is constantly evolving.
}

%------------------------------------------------

\cventry{2013--Current}{Website Developer}{AD Solutions(Co-Founder)}{Manchester}{}{Set up my own business with a classmate over the Summer, which can be found at the URL \url{allenduxburysolutions.co.uk} (currently a work in progress). I aspire to improve my skills and help this business become very successful.}

\cventry{2010--2011}{Summer Intern}{\textsc{Quest Software}}{Singapore}{}{I worked in a team of three to design and implement a solution to digitise all the contact information of the clients and create a search macro that helped the company sort through CVs. At the end of the internship I then gave a demonstration on how to use our solution to the heads of departments.}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Basic}{\textsc{JavaScript},\textsc{php}, GitHub}
\cvitem{Intermediate}{\textsc{Java}, \textsc{html},\textsc{css},\textsc{MySQL},\textsc{Visual Basic}, \LaTeX}


%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------

\section{Projects}

\cventry{2014}{Pair}{}{}{}{I worked in a group of six members and we created a product together called Pair. Pair is a Peer-To-Peer educational application with the intentions of closing the education gap on a global scale, The project took about 6 months and I learnt how to manage my team effectively and found my passion for web development, inspiring me to create my business.}

\cventry{2012}{Extended Essay}{"To what extent is there a mathematical equation for beauty?"}{}{}{I worked independently researching the Golden Ratio and its occurrences in nature and decided to see by performing a survey on over a hundred individuals aged 3-18 whether I could prove that there was a mathematical equation for beauty, I utilised data analysis skills to then extrapolate information from the data and wrote a 5000 word report on the topic and presented my findings to a group of 30 people.}

\cventry{2012}{Minshara Solar System Simulation}{}{}{}{I worked independently to learn Visual Basic and produce a product to be used by the Physics department in my school to aid teaching, I fully documented the project using The Waterfall Model and from this i appreciated the importance of analysis and design in the production of an end product.}




\end{document}
