\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

	\addtolength{\oddsidemargin}{-.475in}
	\addtolength{\evensidemargin}{-.475in}
	\addtolength{\textwidth}{1.00in}

	\addtolength{\topmargin}{-.475in}
	\addtolength{\textheight}{1.00in}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Joseph} % Your first name
\familyname{Allen} % Your last namomape

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Block C Alto}{Salford, M3 6GD}
\mobile{07871556664}
\email{joseph.allen.1994@hotmail.com}
\homepage{joezcool02.github.io}{} % The first argument is the URL for the clickable link, the second argument is the URL displayed in the template - this allows special characters to be displayed such as the tilde in this example

%----------------------------------------------------------------------------------------

\begin{document}



%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage

\recipient{Purple}{} % Letter recipient
\date{\today} % Letter date
\opening{Dear Sir or Madam,} % Opening greeting
\closing{Sincerely yours,} % Closing phrase
\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

\makelettertitle % Print letter title

I am pleased to present my application for a Data Science role at Purple. With my background in mathematics I welcome the academic style that data science work offers. I am familiar with many types of model such as Random Forest and SVM and enjoy streamlining my work with each iteration building template projects to speed up my development. I think my experience in Machine Learning projects will shine at Purple, while I am keen to teach I am just as eager to learn and I hope your culture matches this attitude.

I am a Manchester based Data Scientist with a history in Front-End Development, Digital Marketing and Digital Art. I am now aspiring to further my skills as a Data Scientist. I hope to one day lead a team with my expertise.

My work as a Digital Artist and Front-End Developer bubbles up in my manipulation of Data Science work with a craving for visualization.

I am a strong believer in AGILE methodologies, while appreciating that other methods have their place, and have used SCRUM and Kanban professionally. I hold a firm belief that User Experience and Data Science are the key to the future of success in the technology sector and am always keen to bring these aspects into my development when appropriate. I am confident in running Retrospectives, Stand-ups and reflective meetings as I believe these are vital for improving team happiness and love opportunities to apply these to any team that will let me. I have also assisted in the Open project which encourages people to talk more openly about their emotions in the workplace.

I have organized events of many scale from monthly Digital Art and Data Science meet-ups to much larger scale University events with over 500 attendees. I am always eager to take part in events such as MancJS and MancML and bring any learnings back into the business where possible. I have given a handful of talks such as:
\begin{itemize}
\item CSS as a digital art form
\item How to Fake it until you make it, a Digital Marketing Case Study
\item AHP, a customer-first search
\end{itemize}

I see Data Science problems like crosswords in the back of a newspaper, I enjoy the fun puzzles they bring in my day-to-day life and occasionally participate in Kaggle competitions to assess my skills. I look forward to further utilizing my skills in R and python and am keen to improve my DevOps skills.

Thank you very much for your time and I am thankful for the opportunity of being considered for this position.

Hope to hear from you soon.

\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------
\clearpage



\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{2013--2017}{Bachelor of Computer Science and Mathematics with Industrial Experience}
{The University of Manchester}{}{BA (Hons) 2:1}{}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}
\cventry{2017--Current}{Data Scientist}{LateRooms.com}{Manchester}{}{Working on the Data Science Team has given me an opportunity to add an Agile process in an environment that welcomes it.
\begin{itemize}
\item Hotel Rank Algorithm, a system which generates the rankings of hotels. I implemented multiprocessing to reduce the generation time and created a dashboard in Google Data Studio to monitor parity
\item Analytic Hierarchy Process based customer-first search for the new business platform. And gave a corresponding brown bag
\item Implemented a feature store which lets the Analytics team create higher-level features, and backfills up to two years. Using Docker and cron jobs this stays up to date
\item Occasional short term investigations such as "Does the sentiment of Hotel Descriptions correlate with Hotel Success?" and "How have our hotels changed over time?"
\item Creation of a basic Chatbot using the Watson API to deal with FAQs
\end{itemize}
}

\cventry{2015--2017}{UI Developer}{LateRooms.com}{Manchester}{}{Front-End Developer mainly focusing on the daily additions to the website using HTML,CSS,JS along with some larger deliverables such as: 
\begin{itemize}
\item Co-brands generator. This allows the creation of a new co-brand from a handful of inputs
\item Geo-shapes dashboard, worked closely with the Data Science team to create a React dashboard
\item New platform, currently working on creating a new platform to run many brand off of simultaneously using React with styled components
\end{itemize}}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

\cvitem{Programming}{Python, NumPy, Pandas, PyTest , R, HTML, CSS, JavaScript, Git, GitHub, \LaTeX, Java}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------

\section{Projects}
\cventry{}{Clustering New York Taxi Journeys}{}{}{}{Utilized Principal Component Analysis and its categorical counterpart to cluster taxi journeys into a plain English description.} 

\cventry{}{Hate Speech Classification}{}{}{}{Classifies the subtle differences between rude and offensive tweets using NLP and feature generation.} 

\cventry{}{Change Detection in Live Video}{}{}{}{Allows artists to experiment with various forms of change detection and set the layers to their choice of color, image, video, coded example or live camera.}

\cventry{}{Extended Essay}{"To what extent is there a mathematical equation for beauty?"}{}{}{
Independent research into the golden ratio and its occurrences in nature and used analytical skills to extrapolate information from a survey about perceived beauty.}

\end{document}
