\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
% \moderncvcolor{purple} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\moderncvcolor{grey} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[colorlinks]{hyperref}
\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

	\addtolength{\oddsidemargin}{-.475in}
	\addtolength{\evensidemargin}{-.475in}
	\addtolength{\textwidth}{1.00in}

	\addtolength{\topmargin}{-.475in}
	\addtolength{\textheight}{1.00in}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

% COMMENT FOR ANONYMOUS
\firstname{Joseph} % Your first name
\familyname{Allen} % Your last name

% % All information in this block is optional, comment out any lines you don't need
% \title{Curriculum Vitae}
\mobile{+447849419290}
\email{joseph.allen.1994@hotmail.com}
\homepage{joseph-allen.github.io}{} % The first argument is the URL for the clickable link, the second argument is the URL displayed in the template - this allows special characters to be displayed such as the tilde in this example

%----------------------------------------------------------------------------------------

\begin{document}
%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

% \clearpage
% \date{\today} % Letter date
% \closing{I look forward to speaking with you,} % Closing phrase
% \makelettertitle % Print letter title
% \begin{LARGE}

% Hello, I am pleased to present my application.

% With over 5 years experience working with \textcolor{blue}{React} I am looking for my next opportunity. Front-End Development is a turbulent field, with new and interesting technologies arising every week. As such, I am keen to work on a variety of projects. I am excited to have a project where I can practice my \textcolor{blue}{Typescript} and test-writing. Though I have lead a few small teams sparsely, my ambition is to learn more formal line-management skills.

% I like to establish a solid management foundation for projects I am involved with. I find comfort in an agile workflow. To me, retrospectives, sprint-planning and a mastery-based culture are motivational. On top of my developer skills, I enjoy opportunities to lead teams or assist in the growth of my fellow employees.

% My greatest asset is my ability to perceive and iterate on business processes. It is important that I learn from mistakes, and look with curiosity to the future. I have a history of working on data science projects, of which I enjoy the variety.

% I am comfortable managing online communities, and presenting technical talks to large audiences. I have organised hundreds of tech events, podcasts and talks ranging in topic from \href{https://www.youtube.com/watch?v=blGLY-gX9U4}{``What is synthetic data?''} to \href{https://github.com/joseph-allen/CSS-Brown-Bag}{``CSS as a digital art form''} at  \href{https://www.manchester.ac.uk/}{The University of Manchester}, \href{https://youtu.be/u3hYWLYApoA?t=225}{The University of Liverpool}  and beyond. If hired, I hope to give your business a presence in these communities.

% Please see many more examples of my work on my \href{https://joseph-allen.github.io/}{website}, \href{https://josephallen1234.medium.com}{blog}, or \href{https://github.com/joseph-allen}{GitHub}.

% I look forward to speaking with you.

% Joseph Allen
% \end{LARGE}

%----------------------------------------------------------------------------------------
% \clearpage



\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	BIO
%----------------------------------------------------------------------------------------
I lived in Japan until last year and am looking to return with a Front-End role. I am excited to grow and transition into Full-Stack development, with a goal of becoming a Team Leader. I am familiar with Japanese residence requirements and culture and hold JLPT N5, with plans to sit N4 this summer.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}

\cventry{Apr 2018 \newline Ongoing}{Contract Front-End Developer}{AvocadoGreen}{}{}{
\begin{itemize}
    \item Moreliquid: Fractional CTO bringing emerging assets to market. Researched and selected technology partners to automate investor onboarding. Worked with marketing teams to deliver consistent content, track leads, and automate follow-ups. Won a £100,000 grant, joining Outlier Ventures RWA Base Camp. Launched the world's first tokenised Money Market Euro Fund.
    \item Paragon: Led a team of six developers, building a platform to automate video production using React, Firebase, Redux, and Prisma. Hosted on Netlify and Heroku. Navigated the UK’s COVID Kickstart scheme, placing five developers, and drafted two Innovate UK grant applications.
    \item Ortom: Built for a data science consultancy, increasing traffic tenfold. Developed with React, Gatsby, GraphQL, SCSS, and Netlify CMS.
    \item Raised by Google: Built two React applications and a Flask API for the award-winning interactive art installation, integrating social media-based user interactions.
    \item BilliDrop: Created a white-label lottery application in Next.js, serving over 30 domains. Built with TypeScript, tested with Jest, and deployed on Vercel.
    \item Telux: Led a team of four developers, building the updated front end in React with Redux for state management. Used Jest and Wraith for testing and maintained a Storybook component library.
    \item OurSongRequest: Developed MVP using React, Firebase, Express, and Google Cloud Functions.
    \item Red Meters: Created a platform using React, Gatsby, GraphQL, and Netlify CMS.
    \item LA Priest: Developed the stylized audio player in JavaScript, promoting a launch to over 100,000 listeners.
\end{itemize}
}

\cventry{Mar 2022\newline Sep 2022}{Senior Front-End Developer}{N Brown PLC}{}{}{
\begin{itemize}
\item Developed and maintained credit application features in a Next.js app using React, Redux, and TypeScript.
\item Implemented testing with Jest, React Testing Library, and Cypress.
\item Developed a component library in Storybook.
\item Organised and led developer guilds with daily programming challenges and monthly speaker events.
\end{itemize}
}

\cventry{Sep 2020\newline Mar 2022}{Research Associate}{University of Manchester}{}{}{
\begin{itemize}
\item Delivered training on synthetic data for the UK Data Service.
\item Developed a Codecademy-style data skills training platform using React.
\item Researched ethical use of Twitter data and tracked emerging COVID-19 symptoms using public datasets.
\end{itemize}
}

\cventry{Dec 2015\newline Mar 2018}{Front-End Developer}{LateRooms.com}{}{}{
\begin{itemize}
\item Built an npm package to generate white-label booking platforms, simplifying brand deployment with Node.js and SCSS.
\item Worked with the Data Science team building React Dashboards and delivering a new ranking algorithm which increased revenue by 20 percent.
\item Worked in a team developing a new React-based booking platform.
\end{itemize}
}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{}{Bachelor of Computer Science and Mathematics with Industrial Experience}
{The University of Manchester}{}{BA (Hons) 2:1}{}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Skills}
\cvitem{}{\textcolor{gray}{React, Redux, JavaScript, TypeScript, Node, Jest, RTL, Cypress, Storybook, HTML, SCSS, CSS, GitHub, Gatsby, GraphQL, Python, Firebase, SQL, Netlify, Vercel, Webflow, Heroku, GCP, AWS}}
% \cvitem{}{\textcolor{blue}{React, Redux, JavaScript, TypeScript, Node, Jest, RTL, Cypress, Storybook, HTML, SCSS, CSS, GitHub, Gatsby, GraphQL, Python, Firebase, SQL, Netlify, Vercel, Webflow, Heroku, GCP, AWS}}


\end{document}