\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{casual}
\moderncvcolor{grey}

\usepackage[colorlinks]{hyperref}
\usepackage[scale=0.75]{geometry}

\addtolength{\oddsidemargin}{-.475in}
\addtolength{\evensidemargin}{-.475in}
\addtolength{\textwidth}{1.00in}
\addtolength{\topmargin}{-.475in}
\addtolength{\textheight}{1.00in}

\firstname{Joseph}
\familyname{Allen}

\mobile{+447849419290}
\email{joseph.allen.1994@hotmail.com}
\homepage{joseph-allen.github.io}{}

\begin{document}

\makecvtitle

%----------------------------------------------------------------------------------------
%	BIO
%----------------------------------------------------------------------------------------
Experienced Full-Stack Developer with strong focus on React, TypeScript, and Next.js. I’ve built high-performance, responsive applications in both start-up and enterprise environments, often leading small teams. With a background in the finance sector, I bring domain experience and an eye for quality UI/UX. I hold JLPT N5,  and am familiar with Japanese working culture, and available to relocate from June.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}

\cventry{Apr 2018 \newline Ongoing}{Contract Front-End Developer}{AvocadoGreen}{}{}{
\begin{itemize}
    \item \textbf{SchemeAI:} Built a complex road-mapping dashboard using Next.js and REST APIs. Containerised with Docker, serving 2M+ data points per client.
    \item \textbf{BilliDrop:} Developed a white-label lottery platform using Next.js and TypeScript, deployed across 30+ domains. Wrote unit tests with Jest.
    \item \textbf{Paragon:} Led a 6-person team to build a video automation platform in React and Redux. Managed sprint planning, developer placement, and grant applications.
    \item \textbf{Moreliquid:} Fractional CTO on FinTech startup. Chose tech stack and integrated automation into investor onboarding workflows. Helped win £100K grant; launched first tokenised Euro fund.
    \item \textbf{Telux:} Team lead for React front-end rebuild, using Redux, Jest, and Storybook. Delivered UI aligned with strict design guidelines.
    \item \textbf{Ortom:} Rewrote a React/Gatsby app, resulting in 10x increase in site traffic. Integrated GraphQL and optimised SCSS delivery.
    \item \textbf{Raised by Google:} Delivered interactive social media artwork using React and Flask APIs. Built full stack with real-time integrations.
\end{itemize}
}

\cventry{Sep 2022\newline Mar 2023}{Senior Front-End Developer}{N Brown PLC}{}{}{
\begin{itemize}
\item Contributed to a large-scale Next.js credit application using React, Redux, and TypeScript.
\item Focused on front-end performance, testing, and component architecture.
\item Maintained comprehensive test coverage with Jest, React Testing Library, and Cypress.
\item Developed shared component libraries in Storybook and enforced coding standards.
\item Organised daily dev guild sessions and monthly speaker events to support knowledge sharing and upskilling.
\end{itemize}
}

\cventry{Sep 2020\newline Mar 2022}{Research Associate}{University of Manchester}{}{}{
\begin{itemize}
\item Designed and built a Codecademy-style training platform in React, teaching Python and data handling techniques.
\item Delivered training on synthetic data handling for UK Data Service.
\item Researched ethical data collection and performed analysis on social media trends (e.g., COVID symptom tracking).
\end{itemize}
}

\cventry{Dec 2015\newline Mar 2018}{Front-End Developer / Data Scientist}{LateRooms.com}{}{}{
\begin{itemize}
\item Built front-end interfaces and internal tools in the travel sector using React and Node.js.
\item Developed a reusable white-label booking platform as an npm package.
\item Collaborated with Data Science to deploy a new ranking algorithm, boosting revenue by 20\%.
\item Wrote SQL queries and worked on Google Datastore integrations.
\item Delivered new React-based platform features in an agile, product-led environment.
\end{itemize}
}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{}{Bachelor of Computer Science and Mathematics with Industrial Experience}
{The University of Manchester}{}{BA (Hons) 2:1}{}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Skills}
\cvitem{}{\textcolor{gray}{React, Next.js, TypeScript, Redux, JavaScript, HTML, CSS/SCSS, Node.js, Jest, Cypress, Storybook, GitHub, GraphQL, Firebase, Docker, GCP, AWS, Netlify, Vercel, Webflow, Heroku, SQL, Python}}

\end{document}
