\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{casual}
\moderncvcolor{grey}

\usepackage[colorlinks]{hyperref}
\usepackage[scale=0.75]{geometry}

\addtolength{\oddsidemargin}{-.475in}
\addtolength{\evensidemargin}{-.475in}
\addtolength{\textwidth}{1.00in}
\addtolength{\topmargin}{-.475in}
\addtolength{\textheight}{1.00in}

\firstname{Joseph}
\familyname{Allen}

\mobile{+447849419290}
\email{joseph.allen.1994@hotmail.com}
\homepage{joseph-allen.github.io}{}

\begin{document}

\makecvtitle

%----------------------------------------------------------------------------------------
%	BIO
%----------------------------------------------------------------------------------------
I lived in Japan until last year and seek to return as a Full-Stack Developer. I have extensive experience in both data and web development. My goal is to one day lead a large team of developers. I'm familiar with Japanese residence requirements and hold JLPT N5. I've worked in the travel industry for many years. Available 1st June.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}

\cventry{Apr 2018 \newline Ongoing}{Contract Front-End Developer}{AvocadoGreen}{}{}{
\begin{itemize}
    \item SchemeAI: A road-mapping dashboard built in Next.js and containerised with Docker, with a full REST API, serving over 2 million data points per client.
    \item Moreliquid: Fractional CTO bringing emerging assets to market. Researched and selected technology partners to automate investor onboarding. Worked with marketing teams to deliver consistent content, track leads, and automate follow-ups. Won a £100,000 grant and joined Outlier Ventures RWA Base Camp. Launched the world's first tokenised Money Market Euro Fund.
    \item Paragon: Led a team of six developers, building a platform to automate video production in React, Firebase, Redux, and Prisma. Hosted on Netlify and Heroku. Placed five developers and drafted three grants.
    \item Ortom: A new React app, increasing traffic tenfold. Developed using Gatsby, GraphQL, SCSS, and Netlify.
    \item Raised by Google: Built two React applications and a Flask API for the award-winning interactive art installation, integrating social media-based user interactions.
    \item BilliDrop: Created a white-label lottery application in Next.js, serving over 30 domains. Built with TypeScript, Jest, and Vercel.
    \item Telux: Led four developers, building the updated front end in React, Redux, Jest, Wraith, and Storybook.
    \item OurSongRequest: Developed MVP using React, Firebase, Express, and Google Cloud Functions.
    \item Red Meters: Created a platform using React, Gatsby, GraphQL, and Netlify CMS.
\end{itemize}
}

\cventry{Sep 2022\newline Mar 2023}{Senior Front-End Developer}{N Brown PLC}{}{}{
\begin{itemize}
\item Developed and maintained credit application features in a Next.js app using React, Redux, and TypeScript.
\item Implemented testing with Jest, React Testing Library, and Cypress.
\item Developed a component library in Storybook.
\item Organised and led developer guilds with daily programming challenges and monthly speaker events.
\end{itemize}
}

\cventry{Sep 2020\newline Mar 2022}{Research Associate}{University of Manchester}{}{}{
\begin{itemize}
\item Delivered training on synthetic data for the UK Data Service.
\item Developed a Codecademy-style data skills training platform using React.
\item Researched ethical use of the Twitter data API and tracked emerging COVID-19 symptoms.
\end{itemize}
}

\cventry{Dec 2015\newline Mar 2018}{Front-End Developer, Data Scientist}{LateRooms.com}{}{}{
\begin{itemize}
\item Developed in the hospitality/travel domain, building customer-facing features and internal tooling.
\item Built an npm package to generate white-label booking platforms with Node.js and SCSS.
\item Worked with the Data Science team to build React dashboards and deliver a new ranking algorithm, increasing revenue by 20 percent. Deployed using GCP.
\item Wrote SQL statements to build out complex attributes in Google Datastore.
\item Worked in a team developing a new React-based booking platform.
\end{itemize}
}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{}{Bachelor of Computer Science and Mathematics with Industrial Experience}
{The University of Manchester}{}{BA (Hons) 2:1}{}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Skills}
\cvitem{}{\textcolor{gray}{React, Next.js, Redux, JavaScript, TypeScript, Node, Jest, Cypress, Storybook, HTML, SCSS, CSS, GitHub, Gatsby, GraphQL, Python, Firebase, SQL, Netlify, Vercel, Webflow, Heroku, GCP, AWS, Docker}}

\end{document}
